Should I Airbnb My Property?

### 2017-03-09 abb_Writeup.Rmd
fix occplot bug

   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))

@@

Finally, there are utility costs, $U$, that are borne by the property owner in a short-term leasing strategy but by the tenant in a long-term option.  The State of Victoria estimates energy costs for an apartment at A\$330 per month and for a larger house at A\$520 per month.  For two people in an apartment the cost is approximately A\$5 per person per day and for a four person household in a detached house the cost is around A\$4 per person per day person. For the purposes of estimating utility costs for the short-term rentals we use a mid-point value of A\$4.50 per person per day.  As we don't know total number of guests in each reservation we use a figure of 1.7 guests per bedroom and sum up the total costs for all bookings over the year.

@@

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}

@@

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}

@@

```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.lp='locmaps', fig.ext='png'}

@@

```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts', fig.lp='locbars'}

@@

  # Make Plot
  ggMultiPlots(rawocc, qtlocc, cols=2)

>>>>

   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
   a<-1

@@

Finally, there are utility costs, $U$, that are borne by the property owner in a short-term leasing strategy but by the tenant in a long-term option.  The State of Victoria estimates energy costs for an apartment at A\$330 per month and for a larger house at A\$520 per month.  For two people in an apartment the cost is approximately A\$5 per person per day and for a four person household in a detached house the cost is around A\$4 per person per day person. For the purposes of estimating utility costs for the short-term rentals we use a mid-point value of A\$4.50 per person per day.  As we don't know total number of guests in each reservation we use a figure of 1.5 guests per bedroom and sum up the total costs for all bookings over the year.

@@

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}

@@

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}

@@

```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}

@@

```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}

@@

  # Make Plot
  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
